On Secure Delegation of SampBQP with a Classical Client

### 2020-03-23 preliminaries.tex
Encounter problem in dfn FBQP

We define a sampling version of $\BQP$, $\SampBQP$, based on \cite{aaronson_2013}.

>>>>

We define search and sampling versions of $\BQP$ based on \cite{aaronson_2013}.

\begin{definition} [search problem]
	A search problem $R$ is a collection of nonempty sets $(A_x)_{x\in\set{0, 1}^*}$, one for each input string $x\in\set{0, 1}^*$, where $A_x$... \Ethan{Great, interface doesn't line up correctly}
\end{definition}
